Andres Karjus

### 2017-12-31 index.Rmd
fixed toc
links fixed

---
title: "Andres Karjus"
output: 
  html_document: 
    theme: spacelab
    toc: yes
---
<style>
body {
text-align: justify}
</style>

@@

<IMG SRC="IMG_2657.jpg" ALIGN="right" BR CLEAR="left" style="margin-left:10px"; /> 
I am a PhD student in linguistics based at the [Centre for Language Evolution at the University of Edinburgh](http://www.lel.ed.ac.uk/cle/), working on evolutionary variant selection in language with [Kenny Smith](www.lel.ed.ac.uk/~kenny), [Simon Kirby](www.lel.ed.ac.uk/~simon) and [Richard A. Blythe](https://www2.ph.ed.ac.uk/~rblythe3/), utilizing massive corpora and natural language processing to hunt traces of selection and competition between elements of language. My research is supported by a Kristjan Jaak scholarship from the Archimedes Foundation of Estonia (incidentally which is where I am from).

@@

* Andres Karjus, Richard A. Blythe, Simon Kirby, Kenny Smith, 2018. Topical advection as a baseline model for diachronic lexical dynamics. Proceedings of The Society for Computation in Linguistics. Volume 1. [extended abstract, open access](http://scholarworks.umass.edu/scil/) [full paper in prep]
* Martin Ehala, Andres Karjus, [accepted]. Testing an agent based model of language choice on sociolinguistic survey data. Language Dynamics and Change.
*	Martin Haspelmath, Andres Karjus, 2017. Explaining asymmetries in number marking: Singulatives, pluratives and usage frequency. Linguistics, volume 55, issue 6. [online version](https://www.degruyter.com/view/j/ling.2017.55.issue-6/ling-2017-0026/ling-2017-0026.xml)  [preprint](https://www.academia.edu/25032500/Explaining_asymmetries_in_number_marking_Singulatives_pluratives_and_usage_frequency)
*	Andres Karjus, 2015. Through the Spyglass of Synchrony: Grammaticalization of the Exterior Space in the Eastern Circum-Baltic. In: Hilpert, Martin, Östman, Jan-Ola, Mertzlufft, Christine, Rießler, Michael, Duke, Janet (eds.), Advances in Nordic Linguistics. De Gruyter Mouton.
[google books](https://books.google.ee/books?id=BPheCAAAQBAJ)
*	Andres Karjus (editor), 2013. Areal linguistics, Grammar and Contacts. Special issue of the Journal of Estonian and Finno-Ugric Linguistics, 4-2. Tartu: University of Tartu Press. 
[open access](http://jeful.ut.ee/index.php/JEFUL/issue/view/2013.4.2)
* Petar Kehayov, Eva Saar, Miina Norvik, Andres Karjus, 2013. Hääbuva kesklüüdi murde jälgedel suvel 2012 [On the footsteps of vanishing Central Lude in the summer of 2012]. Yearbook of the Estonian Mother Tongue Society, Vol. 58. [open access](http://www.kirj.ee/public/ESA/2012/esa_58-2012-58-101.indd.pdf)
*	Andres Karjus, 2012. Outdoors on the Shores of the Baltic: Gradience in the Grammaticalization of the Exterior-Region. Journal of Estonian and Finno-Ugric Linguistics 3-1, pp. 209-226. [open access](http://jeful.ut.ee/public/files/Karjus%20209-226.pdf) [short paper based on MA thesis]

@@

I will be attending the [LSA2018](https://www.linguisticsociety.org/event/lsa-2018-annual-meeting) and presenting a poster at the co-occurring inaugural meeting of the [Society for Computation in Linguistics](https://blogs.umass.edu/scil/scil-2018/). I will also be giving a talk at [Evolang 2018](evolang.cles.umk.pl).

>>>>

---
title: "Andres Karjus"
output: 
  html_document: 
    theme: spacelab
    toc: yes
    toc_depth: 1
---

<style>
body {
text-align: justify}
</style>

@@

<IMG SRC="IMG_2657.jpg" ALIGN="right" BR CLEAR="left" style="margin-left:10px"; /> 
I am a PhD student in linguistics based at the [Centre for Language Evolution at the University of Edinburgh](http://www.lel.ed.ac.uk/cle/), working on evolutionary variant selection in language with [Kenny Smith](http://www.lel.ed.ac.uk/~kenny), [Simon Kirby](http://www.lel.ed.ac.uk/~simon) and [Richard A. Blythe](http://www2.ph.ed.ac.uk/~rblythe3/), utilizing massive corpora and natural language processing to hunt traces of selection and competition between elements of language. My research is supported by a Kristjan Jaak scholarship from the Archimedes Foundation of Estonia (incidentally which is where I am from).

@@

* Andres Karjus, Richard A. Blythe, Simon Kirby, Kenny Smith, 2018. Topical advection as a baseline model for diachronic lexical dynamics. Proceedings of The Society for Computation in Linguistics. Volume 1. | [extended abstract, open access](http://scholarworks.umass.edu/scil/) [full paper in prep]
* Martin Ehala, Andres Karjus, [accepted]. Testing an agent based model of language choice on sociolinguistic survey data. Language Dynamics and Change.
*	Martin Haspelmath, Andres Karjus, 2017. Explaining asymmetries in number marking: Singulatives, pluratives and usage frequency. Linguistics, volume 55, issue 6. | [online version](https://www.degruyter.com/view/j/ling.2017.55.issue-6/ling-2017-0026/ling-2017-0026.xml)  | [preprint](https://www.academia.edu/25032500/Explaining_asymmetries_in_number_marking_Singulatives_pluratives_and_usage_frequency)
*	Andres Karjus, 2015. Through the Spyglass of Synchrony: Grammaticalization of the Exterior Space in the Eastern Circum-Baltic. In: Hilpert, Martin, Östman, Jan-Ola, Mertzlufft, Christine, Rießler, Michael, Duke, Janet (eds.), Advances in Nordic Linguistics. De Gruyter Mouton.
| [google books](https://books.google.ee/books?id=BPheCAAAQBAJ)
*	Andres Karjus (editor), 2013. Areal linguistics, Grammar and Contacts. Special issue of the Journal of Estonian and Finno-Ugric Linguistics, 4-2. Tartu: University of Tartu Press. 
| [open access](http://jeful.ut.ee/index.php/JEFUL/issue/view/2013.4.2)
* Petar Kehayov, Eva Saar, Miina Norvik, Andres Karjus, 2013. Hääbuva kesklüüdi murde jälgedel suvel 2012 [On the footsteps of vanishing Central Lude in the summer of 2012]. Yearbook of the Estonian Mother Tongue Society, Vol. 58. | [open access](http://www.kirj.ee/public/ESA/2012/esa_58-2012-58-101.indd.pdf)
*	Andres Karjus, 2012. Outdoors on the Shores of the Baltic: Gradience in the Grammaticalization of the Exterior-Region. Journal of Estonian and Finno-Ugric Linguistics 3-1, pp. 209-226.

@@

I will be attending the [LSA2018](https://www.linguisticsociety.org/event/lsa-2018-annual-meeting) and presenting a poster at the co-occurring inaugural meeting of the [Society for Computation in Linguistics](https://blogs.umass.edu/scil/scil-2018/). I will also be giving a talk at [Evolang 2018](http://evolang.cles.umk.pl).
